### 2012-12-12 inst/examples/multidimensional.Rmd
another example (includes some data in the higher range) #7

```{r phase-space}
inits <- as.matrix(expand.grid(seq(0.05,0.6,length=11), seq(0.05,0.6, length=11)))
df <- lapply(1:round(length(inits[,1])), function(j){
  X[1,] = inits[j,]
  for(i in 1:(Tmax-1))
    X[i+1,] = mumby(X[i,],0.2)
  data.frame(time = 1:Tmax, X)
  })
df2 <- melt(df, id=c("time", "M", "C"))
ggplot(df2) + geom_line(aes(M, C, group=L1)) + 
  geom_point(data = subset(df2, time==1), aes(M, C, group=L1), col="red")
```

@@

```{r}
ggplot(tgp_dat)  + geom_ribbon(aes(x1,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x1,y)) + geom_point(data=obs, aes(x1,y)) 
```

```{r}
ggplot(tgp_dat)  + geom_ribbon(aes(x2,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x2,y)) + geom_point(data=obs, aes(x2,y)) 
```

>>>>

```{r phase-space, cache=TRUE, cache.path="phasespace/"}
inits <- as.matrix(expand.grid(seq(0.05,0.6,length=11), seq(0.05,0.6, length=11)))
df <- lapply(1:round(length(inits[,1])), function(j){
  X[1,] = inits[j,]
  for(i in 1:(Tmax-1))
    X[i+1,] = mumby(X[i,],0.2)
  data.frame(time = 1:Tmax, X)
  })
df2 <- melt(df, id=c("time", "M", "C"))
ggplot(df2) + geom_line(aes(M, C, group=L1)) + 
  geom_point(data = subset(df2, time==1), aes(M, C, group=L1), col="red")
```

@@

```{r x1}
ggplot(tgp_dat)  + geom_ribbon(aes(x1,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x1,y)) + geom_point(data=obs, aes(x1,y)) 
```

```{r x2}
ggplot(tgp_dat)  + geom_ribbon(aes(x2,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x2,y)) + geom_point(data=obs, aes(x2,y)) 
```
